### 2014-10-24 motivation.tex

The definitions are a straight forward encoding of the expected behavior.
The operation definitions presented here only capture the convergence
properties of the replicated data type, and are not concerned with the
consistency properties, which is expressed through the contract language.

>>>>

The definitions are a straight forward encoding of the expected behavior.
Quelea programming model provides the programmer complete freedom regarding the
semantics and desired convergence property of the replicated data type, and
indeed, we can encode the well-known CRDTs~\cite{SSS} in a declarative fashion.
Observe that the operation definitions presented here only capture the
convergence properties of the replicated data type, and are not concerned with
the consistency properties, which is expressed through the contract language.
